Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-21 stp/paper_aaai/main.tex
Trying to shrink, rewrote section 5.1 and 5.2

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=1.5,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-3) {Organisation};
	\node[class] (ev) at (3.5,1) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-3) {City};
	\node[class] (st) at (5,-3) {State};

@@

	\path[hasaC,->] (co) edge [] 
	node [midway, above, sloped] {location} (pl) ;

@@

	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 10] 
	node [midway, above, sloped] {name} (-0.5,2);
	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {birthDate} (0,2);

	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {name} (-1,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {phone} (0,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {email} (1,-5);

	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {startDate} (2.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {title} (4.5,3.2);

@@

In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
Properties are classified into object properties, which relate two individuals, and datatype properties, which relate indivuduals to literal values.
An example of an ontology is given in Fig.~\ref{FIG:onto}. 
Here, an individual of the class ``Organisation'' can be related to an individual of the class ``Person'' via object properties ``ceo'' or ``worksFor'', and it can have a data property ``name''. 
We also consider a special ``subclass'' (or ``is-a'') type of object properties.
For 
example, ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.
\npr{check}

@@

	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
	\node[data] (peb) at (4.3,-1) {\scriptsize Person.birthDate};
	\node[data] (cin) at (1,-1) {\scriptsize City.name};
	\node[data] (stn) at (-1,-1) {\scriptsize State.name};
	\node[data] (con) at (6,-1) {\scriptsize Org.name};

@@

	\path[draw,hasaA,->] (st) -- (stn);
\end{scope}
\begin{scope}[yshift=-60]
	\node[class] (pl) at (-1,0)  {\small City};
	\node[class] (pe) at (3,0)  {\small Person};
	\node[class] (co) at (1,0) {\small Org.};
	\node[class] (ev) at (6,0) {\small Event};

	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1) {\scriptsize Event.endDate};
	\node[data] (con) at (1,-1) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-1) {\scriptsize City.name};

@@

	\path[hasaC,->] (co) edge [bend left = -10] 
	node [midway, above, sloped] {location} (pl) ;

@@

We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source description. 
We use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, 
but only one or a few will capture the intended meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

\section{ML for Training on Source Descriptions \label{SEC:ML}\ddg{Better title 
than this 
please...}}

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source \ddg{Which features?} and associate the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
confidence? If so, 
what is $k$?}
\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}

@@

The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
\begin{enumerate}
\item Adding the known semantic models.
\item Adding the semantic types learned for the target source. \ddg{TODO: see 
Important note above}
\item Expanding the graph using the domain ontology $\mathcal{O}$.
\end{enumerate}

@@

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

@@

	\node[data] (pen) at (2.3,1) {\scriptsize Person1.name};
	\node[data] (peb) at (4.2,1) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (0.7,1) {\scriptsize City1.name};
	\node[data] (stn) at (-1,1) {\scriptsize State.name};
	\node[data] (con) at (6,1) {\scriptsize Org1.name};

@@

% % % CC2
\def\ysh{-2.5};

@@

	\node[data] (pen) at (2.3,-1+\ysh) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event.endDate};
	\node[data] (con) at (0.7,-1+\ysh) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City2.name};

@@

	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-45,in=120] (PL);
	\path[draw,isa,->,orange!30!white] (pl2) edge[out=90,in=180] (PL);
	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=150] (PL);

@@

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $S_T$.
This is known as Transactional Frequent Graph Pattern Mining, which contains the subgraph 
isomorphism, known to be NP-complete.
The frequency of a pattern is an anti-monotonous measure, meaning that bigger patterns will have lower supports than their subgraphs.
We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching. Should it be better in related work?}

@@

Given a graph $G =
(V, E)$ and a subset of its nodes $T \subseteq V$ , called \emph{terminals}, a 
Steiner Tree $G_s = (V_s, E_s )$ is a tree such that $T \subseteq V_s \subseteq 
V$ and $E_s \subseteq E$. In other words, $G_s$ spans all the nodes in $T$ and 
may include additional nodes from $V$, in particular to ensure the 
connectedness of the constructed tree. The Steiner Tree Problem 
(STP) is stated as follows: given $G$ and a weight function $w_f : E 
\mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
by Karp \cite{Karp1972}.

To formulate the \relonto{} schema mapping problem as a STP for a new source 
$s^\star$, we construct the 
\emph{integration graph} $~\mathcal{I}_\mathcal{O}^{s^\star} = 
(\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, with 
nodes $\mathcal{V}_\mathcal{O}^{s^\star} = \mathcal{V_O} \cup 
\mathcal{A}_{s^\star}$, 
edges $\mathcal{E}_\mathcal{O}^{s^\star}$.

@@

	\node[data] (stn1) at (-3.9,-1) {\scriptsize S.n};
	\node[data] (cin1) at (-3.1,-1) {\scriptsize C1.n};
	\node[data] (pen1) at (-2.3,-1) {\scriptsize P1.n};
	\node[data] (peb1) at (-1.5,-1) {\scriptsize P1.b};
	\node[data] (con1) at (-0.7,-1) {\scriptsize O1.n};

@@

% % % CC2
\def\ysh{0};

@@

\node[rectangle, rounded corners,very thick,draw, dashed, 
brown!40!red!40!white,minimum 
height=18, minimum 
width=220] 
(source) at 
(0,-3) 
{};
\node[brown!40!red!40!white] 
(source) at 
(-4.1,-3) 
{$s^\star$:};
	\node[att] (a1) at (-3,-3) {\small Surame};
	\node[att] (a2) at (-1,-3) {\small Workplace};
	\node[att] (a3) at (1,-3) {\small Date};
	\node[att] (a4) at (3,-3) {\small Location};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
abbreviated but 
correspond to the ones shown in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\end{figure}

@@

The goal is to build a subgraph $T^\star= (V^\star, E^\star)$ 
of the integration graph 
$\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The solution 
$T^\star$ will 
be used to build the source description $\delta^\star = (s^\star, m^\star, 
\phi^\star)$. 
In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
corresponds to the semantic model, and 
$(\mathcal{A}_{s^\star},\mathcal{M}_\mathcal{O}^{s^\star} \cap E^\star)$ 
corresponds to 
the attribute mapping function.

The solution $T^\star$ must satisfy the following constraints:
\begin{enumerate}
	\item $T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$
	\item $T^\star$ must be a tree (connected acyclic graph)
	\item $\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$
	\item $\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$
	%\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
	%\{0,2\}$
	\item $\forall n \in \mathcal{D_{G_O}} \cap V^\star, 
	degree(a) = 2$
\end{enumerate}

@@

\section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}

\subsection{Definitions}
A Constraint Satisfaction Problem (CSP) is a tuple $P = (\boldsymbol{v},D,C)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $D$ is a set of unary constraints over 
$\boldsymbol{v}$ specifying 
the \emph{domain} of these variables, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$.
A valuation $\theta(\boldsymbol{v})$ is a mapping from the set of variables to 
values in $D$. 
If there exist a valuation $\theta^\star$ such that all 
variables map 
to exactly one value, and all the constraints in $D\cup C$ are satisfied by the 
valuation, then $\theta^\star$ is a \emph{solution} to $P$.

A Constraint Optimization Problem (COP) is a CSP with an additional 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ and a 
\emph{sign} which is either \verb|minimize| or \verb|maximize|.

A typical example of COP is the Traveling Salesman Problem, where we need to 
find a route that visits all cities in a region exactly one and is of minimal 
length.

\subsection{Constraint Programming}
Constraint Programming (CP) allows the user to model a CSP or COP and give it 
to a 
solver that will find a solution to the CSP, or will report unsatisfiability if 
no solution exists. In the case of COPs, the solver will try to optimize 
the objective function and prove optimality as well.

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ from $D$ in turn. At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change it's 
last decision. The choice of the order of the variables to be assigned, and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}.

Since only using a backtracking algorithm would have a prohibitive cost, CP 
uses a combination of search and \emph{propagation}. The latter is achieved by 
\emph{propagating} the last decision made via specialized algorithms called 
\emph{propagators}. A propagator is a function $p : (v, D_v) \mapsto D_v'$ that 
takes a subset of the variables of the problem $v \subseteq \boldsymbol{v}$ and 
the domain of those variables $D_v$ and returns a new domain for these 
variables 
such that $D_v' \sqsubseteq D$. That is, a propagator removes values form the 
domains of variables (when possible). For a propagator to be correct, it must 
not remove a value of the domain of a variable if such value could participate 
in a solution given the decisions already made.

\emph{Global constraints} are higher order constraints that enforce a 
complicated 
constraint over a set of variables. Typical examples of this is enforcing that 
a set of variables take different values, or that they describe a path a in a 
graph. Although it is possible to express these constraints with a conjunction 
of simple constraints, it is often the case that specific algorithms for these 
constraints perform substantially better than a decomposition approach (e.g. 
\cite{regin1994filtering}). A wide 
list of these global constraints can be found in \cite{beldiceanu2012global}.

>>>>

\usepackage{tikz}
\tikzset{every picture/.style={font issue=\small},
         font issue/.style={execute at begin picture={#1\selectfont}}
        }
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=0.3,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

\newcommand{\ignore}[1]{}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-2) {Organisation};
	\node[class] (ev) at (3,0.2) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-2.5) {City};
	\node[class] (st) at (5,-2.5) {State};

@@

	\path[hasaC,->] (co) edge [] 
	node [near start, above, sloped] {location} (pl) ;

@@

	\path[draw,hasaA,->] (pe) edge [decorate,out=140,in=0] 
	node [midway, above, sloped] {name} (-0.9,0.5);
	\path[draw,hasaA,->] (pe) edge [decorate,out=100,in=0] 
	node [midway, above, sloped] {birthDate} (-0.9,1);

	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {name} (-1,-3);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {phone} (0,-3.2);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {email} (1.4,-3);

	\path[draw,hasaA,->] (ev) edge [decorate,out=70,in=200] 
	node [midway, above, sloped] {startDate} (3.8,1);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {endDate} (4.5,0.8);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {title} (5,0.2);

@@

In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
Properties are classified into \emph{object properties}, which relate two 
individuals, 
and \emph{datatype properties}, which relate individuals to literal values.
An example of an ontology is given in Fig.~\ref{FIG:onto}. 
Here, an individual of the class ``Organisation'' can be related to an individual of the class ``Person'' via object properties ``ceo'' or ``worksFor'', and it can have a data property ``name''. 
We also consider a special ``subclass'' (or ``is-a'') type of object properties.
For 
example, ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.

@@

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person.birthDate};
	\node[data] (cin) at (1,-0.7) {\scriptsize City.name};
	\node[data] (stn) at (-1,-0.7) {\scriptsize State.name};
	\node[data] (con) at (6,-0.7) {\scriptsize Org.name};

@@

	\path[draw,hasaA,->] (st) -- (stn);
\end{scope}
\begin{scope}[yshift=-40]
	\node[class] (pl) at (-1,0)  {\small City};
	\node[class] (pe) at (3,0)  {\small Person};
	\node[class] (co) at (1,0) {\small Org.};
	\node[class] (ev) at (6,0) {\small Event};

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-0.7) {\scriptsize Event.endDate};
	\node[data] (con) at (1,-0.7) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-0.7) {\scriptsize City.name};

@@

	\path[hasaC,->] (co) edge [bend left = 0] 
	node [midway, above, sloped] {location} (pl) ;

@@

We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source description. 
We use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, 
but only one or a few will capture the intended meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
$m^\star$ and the semantic model $m^\dag$ that the user considers correct. 
%\npr{definitions for precision and recall}

\section{ML for Training on Source Descriptions \label{SEC:ML}}

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

Note that we keep all the matches, regardless of the confidence fo the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics to then simplify the task of 
finding the semantic model. \ddg{CHECK}

%\ddg{IMPORTANT: Do we keep  all of them, or only the top $k$ with most 
%confidence? If so, 
%what is $k$?}
%\npr{We keep all, that is the crucial difference from Karma which does some 
%voodoo heuristic filtering}

@@

The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
%\begin{enumerate}
$(i)$ %\item 
Adding the known semantic models
$(ii)$ %\item 
Adding the semantic types learned for the target source \ddg{If we keep 
all matches, isn't this just adding all the semantic types?}
%\item 
$(iii)$ Expanding the graph using the domain ontology $\mathcal{O}$.
%\end{enumerate}

@@

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?}

@@

	\node[data] (pen) at (2.3,0.7) {\scriptsize Person1.name};
	\node[data] (peb) at (4.2,0.7) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
	\node[data] (stn) at (-1,0.7) {\scriptsize State.name};
	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};

@@

% % % CC2
\def\ysh{-2};

@@

	\node[data] (pen) at (2.3,-0.7+\ysh) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event.endDate};
	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-0.7+\ysh) {\scriptsize City2.name};

@@

	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-25,in=130] (PL);
	\path[draw,isa,->,orange!30!white] (pl2) edge[out=50,in=180] (PL);
	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=160] (PL);

@@

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $S_T$.
This is known as Transactional Frequent Graph Pattern Mining, which contains the subgraph 
isomorphism, known to be NP-complete.
The frequency of a pattern is an anti-monotonous measure, meaning that bigger 
patterns will have lower supports than their subgraphs. \ddg{Define support}
We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. 
\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
cite my work on how databases perform for graph pattern matching. Should it be 
better in related work?}

@@

Given a graph $G =
(V, E)$ and a subset of its nodes $T \subseteq V$, a 
Steiner Tree $G_s = (V_s, E_s )$ is a tree such that $T \subseteq V_s \subseteq 
V$ and $E_s \subseteq E$. In other words, $G_s$ spans all the nodes in $T$ and 
may include additional nodes from $V$, in particular to ensure the 
connectedness of the constructed tree. The Steiner Tree Problem 
(STP) is stated as follows: given $G$ and a weight function $w_f : E 
\mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
by Karp \cite{Karp1972}.

To formulate the \relonto{} schema mapping problem as a STP for a new source 
$s^\star$, we construct the 
\emph{integration graph} $~\mathcal{I}_\mathcal{O}^{s^\star} = 
(\mathcal{V}_\mathcal{O}^{s^\star},\mathcal{E}_\mathcal{O}^{s^\star})$, where  
$\mathcal{V}_\mathcal{O}^{s^\star} = \mathcal{V_O} \cup 
\mathcal{A}_{s^\star}$.

@@

	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S.n};
	\node[data] (cin1) at (-3.1,-0.9) {\scriptsize C1.n};
	\node[data] (pen1) at (-2.3,-0.9) {\scriptsize P1.n};
	\node[data] (peb1) at (-1.5,-0.9) {\scriptsize P1.b};
	\node[data] (con1) at (-0.7,-0.9) {\scriptsize O1.n};

@@

% % % CC2
\def\ysh{0.1};

@@

\node[rectangle, rounded corners,very thick,draw, dashed, 
brown!40!red!40!white,minimum 
height=18, minimum 
width=220] 
(source) at 
(0,-2) 
{};
\node[brown!40!red!40!white] 
(source) at 
(-4.1,-2) 
{$s^\star$:};
	\node[att] (a1) at (-3,-2) {\small Surame};
	\node[att] (a2) at (-1,-2) {\small Workplace};
	\node[att] (a3) at (1,-2) {\small Date};
	\node[att] (a4) at (3,-2) {\small Location};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights and only show the most likely 
matches for clarity. Data node
are the same as in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\end{figure}

@@

The goal is to build a subgraph $T^\star= (V^\star, E^\star)$ of
$\mathcal{I}_\mathcal{O}^{s^\star}$ for the new source $s^\star$. The solution 
$T^\star$ will 
be used to build the source description $\delta^\star$. 
In particular, $(\mathcal{V_O} \cap V^\star,\mathcal{E_O} \cap E^\star)$ 
corresponds to the semantic model, and 
$(\mathcal{A}_{s^\star},\mathcal{M}_\mathcal{O}^{s^\star} \cap E^\star)$ 
corresponds to 
the attribute mapping function.

The solution $T^\star$ must satisfy the following constraints:
%\begin{enumerate}
	$(i)$ %\item 
	$T^\star$ must be a subgraph of $\mathcal{I}_\mathcal{O}^{s^\star}$,
	$(ii)$ %\item 
	$T^\star$ must be a tree (connected acyclic graph),
	$(iii)$ %\item 
	$\forall a \in \mathcal{A}_{s^\star}, a\in V^\star$,
	$(iv)$ %\item 
	$\forall a \in \mathcal{A}_{s^\star}, degree(a) = 1$,
	%\item $\forall n \in \mathcal{D_{G_O}}, degree(a) \in 
	%\{0,2\}$
	$(v)$ %\item 
	$\forall n \in \mathcal{D_{G_O}} \cap V^\star, degree(a) = 2$
%\end{enumerate}

@@

\section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
\subsection{Definitions}
A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
(w.l.o.g.) minimized. 
A valuation such that all variables in $\boldsymbol{v}$ map 
to exactly one value, and all the constraints in $C$ are satisfied by the 
valuation is a \emph{solution} to $P$. A solution $\theta$ is optimal if$\not 
\exists \theta', \theta'(\boldsymbol{v}) < \theta(\boldsymbol{v})$.

\ignore{
A typical example of COP is the Traveling Salesman Problem, where we need to 
find a route that visits all cities in a region exactly one and is of minimal 
length.
}

%\subsection{Constraint Programming}
Constraint Programming (CP) allows the user to model a COP and give it 
to a solver that will find solutions to the COP and while optimizing 
the objective function (and prove optimality).

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ in turn. At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change it's 
last decision. \ignore{The choice of the order of the variables to be assigned, 
and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}}.

Since only using a backtracking algorithm would have a prohibitive cost, CP 
uses a combination of search and \emph{propagation}. The latter is achieved by 
\emph{propagating} the last decision made via specialized algorithms called 
\emph{propagators}. A propagator is a function that removes inconsistent values 
form the domains of variables. That way, values that cannot appear in a 
solution givent eh current set of decisions are never tried by the search.

\emph{Global constraints} are higher order constraints that enforce a 
complex 
constraint over a set of variables. These are typically implemented with 
propagators that use specific algorithms for these 
constraints and perform substantially better than a decomposition approach
\cite{regin1994filtering,beldiceanu2012global}.

\ignore{
\subsubsection{Example} Consider the toy problem $P$ over variables $a$ and $b$ 
such that $a \in \{2,3,4\}$, $b \in \{1,2,3\}$. Let $C = \{a + 2b \leq 4, a 
\neq b\}$ be the constraints. If the search step decides that $a = 
2$, then $(i)$ $a \neq b \Rightarrow b \in \{1,3\}$ and $(ii)$ $a + 2b \leq 4  
\Rightarrow b \in \{1\}$. Thus we automatically know that $b = 1$ without never 
trying any other of its original possible values. $\square$
}
